Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-30 draft/ms_v5.tex
Add table heads
Appendix: quality control

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
    \hline
    Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
    \cline{2-12}
    Magnitude & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) \\
    \hline

@@

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.021 &   0.019 &   0.019 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.008 &   0.004 & \n0.004 & \n0.006 \\
    \hline 
    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.026 &   0.025 &   0.020 &   0.020 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.037 &   0.033 &   0.022 &   0.021 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.005 &   0.002 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.054 &   0.051 &   0.031 &   0.031 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.003 &   0.001 & \n0.001 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.077 &   0.075 &   0.058 &   0.057 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.002 & \n0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.105 &   0.105 &   0.109 &   0.123 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.009 & \n0.002 &   0.011 & \n0.002 \\
    \hline
    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.117 &   0.137 &   0.189 &   0.221 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.005 &   0.007 &   0.064 & \n0.063 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 3 : Magnitudes for cModel
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
    \hline
    Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
    \cline{2-12}
    Magnitude & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) \\
    \hline

@@

    \rowcolor[gray]{.85} 22.0 & \smag{} & 0.019 & 0.019  & 0.024 & 0.031 & 0.017 & 0.014 & 0.014 & 0.021 & 0.021 & 0.023 \\
    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.006  & 0.012 & 0.009 & 0.002 & 0.002 & 0.002 & 0.003 & 0.006 & 0.008 \\
    \hline

    \rowcolor[gray]{1.0} 23.0 & \smag{} &   0.161 & 0.138  & 0.147 & 0.167 & 0.168 & 0.174 & 0.182 & 0.185 & 0.197 & 0.194 \\
    \rowcolor[gray]{1.0}      & \mmag{} & \n0.004 & 0.029  & 0.033 & 0.033 & 0.036 & 0.021 & 0.018 & 0.028 & 0.014 & 0.020 \\
    \hline

@@

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 20.0 & \scolor{} &   0.068 & 0.051 &   0.072 &   0.046 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
    \hline 
    \rowcolor[gray]{1.0} 21.0 & \scolor{} &   0.080 & 0.059 &   0.062 &   0.040 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
    \hline
    \rowcolor[gray]{.85} 22.0 & \scolor{} &   0.089 & 0.072 &   0.071 &   0.059 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 23.0 & \scolor{} &   0.105 & 0.090 &   0.109 &   0.103 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 24.0 & \scolor{} &   0.136 & 0.127 &   0.175 &   0.170 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 25.0 & \scolor{} &   0.179 & 0.185 &   0.227 &   0.241 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} colors using 
        $(g-i)$ and $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) 
        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:cmodel_color}.
        Other details are the same with Table \ref{tab:psfcolor}.
    }
        \label{tab:cmodelcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

@@

@@

    The HSC survey defines the full--depth \& full--color regions (\texttt{FDFC}) to
    ensure the data used for science reach the expected number of exposures in each
    band
    ($\mathtt{(\#gri\ \geq\ 4)\ and\ (\#yz\ \geq\ 6)\ and\ (Limiting\ imag> 25.6)}$;
    see \citealt{HSCDR1} for details).
    Since the two \tracts{} we used in this work are almost entirely covered in
    the \texttt{FDFC} region, we did not apply this cut.
    We did apply the following cuts to the matched synthetic objects.

@@

        \item[ ] \texttt{ idetect\_is\_primary==True }
        \item[ ] \texttt{ ideblend\_skipped==False }
        \item[ ] \texttt{ iflags\_badcentroid==False }
        \item[ ] \texttt{ icentroid\_sdss\_flags==False }
        \item[ ] \texttt{ iflags\_pixel\_edge==False }
        \item[ ] \texttt{ iflags\_pixel\_interpolated\_center==False }
        \item[ ] \texttt{ iflags\_pixel\_saturated\_center==False }
        \item[ ] \texttt{ iflags\_pixel\_cr\_center==False }
        \item[ ] \texttt{ iflags\_pixel\_bad==False }
        \item[ ] \texttt{ iflags\_pixel\_suspect\_center==False }
        \item[ ] \texttt{ iflags\_pixel\_clipped\_any==False }
        \item[ ] \texttt{ iflags\_pixel\_bright\_object\_center==False }

>>>>

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
    \hline 
    \rowcolor[gray]{.85} \multicolumn{12}{|c|}{\large{Table}: Summary of \forced{} PSF Magnitude} \\
    \hline \hline 
    Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
    \cline{2-12}
    Magnitude & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) \\
    \hline

@@

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} PSF Colors} \\
    \hline \hline 
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.021 &   0.019 &   0.019 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.008 &   0.004 & \n0.004 & \n0.006 \\
    \hline 
    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.026 &   0.025 &   0.020 &   0.020 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.037 &   0.033 &   0.022 &   0.021 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.005 &   0.002 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.054 &   0.051 &   0.031 &   0.031 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.003 &   0.001 & \n0.001 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.077 &   0.075 &   0.058 &   0.057 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.002 & \n0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.105 &   0.105 &   0.109 &   0.123 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.009 & \n0.002 &   0.011 & \n0.002 \\
    \hline
    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.117 &   0.137 &   0.189 &   0.221 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.005 &   0.007 &   0.064 & \n0.063 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 3 : Magnitudes for cModel
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
    \hline
    \rowcolor[gray]{.85} \multicolumn{12}{|c|}{\large{Table}: Summary of \forced{} \cmodel{} Magnitude} \\
    \hline \hline 
    Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
    \cline{2-12}
    Magnitude & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) \\
    \hline

@@

    \rowcolor[gray]{.85} 22.0 & \smag{} &   0.161 & 0.138  & 0.147 & 0.142 & 0.154 & 0.153 & 0.165 & 0.167 & 0.178 & 0.169 \\
    \rowcolor[gray]{.85}      & \mmag{} & \n0.004 & 0.029  & 0.033 & 0.050 & 0.004 & 0.040 & 0.038 & 0.045 & 0.044 & 0.048 \\
    \hline

    \rowcolor[gray]{1.0} 23.0 & \smag{} & 0.152 & 0.147  & 0.167 & 0.168 & 0.168 & 0.174 & 0.182 & 0.185 & 0.197 & 0.194 \\
    \rowcolor[gray]{1.0}      & \mmag{} & 0.021 & 0.040  & 0.033 & 0.036 & 0.017 & 0.021 & 0.018 & 0.028 & 0.014 & 0.020 \\
    \hline

@@

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} \cmodel{} Colors} \\
    \hline \hline 
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 20.0 & \scolor{} &   0.068 & 0.051 &   0.072 &   0.046 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
    \hline 
    \rowcolor[gray]{1.0} 21.0 & \scolor{} &   0.080 & 0.059 &   0.062 &   0.040 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
    \hline
    \rowcolor[gray]{.85} 22.0 & \scolor{} &   0.089 & 0.072 &   0.071 &   0.059 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 23.0 & \scolor{} &   0.105 & 0.090 &   0.109 &   0.103 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 24.0 & \scolor{} &   0.136 & 0.127 &   0.175 &   0.170 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 25.0 & \scolor{} &   0.179 & 0.185 &   0.227 &   0.241 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} colors using 
        $(g-i)$ and $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) 
        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:cmodel_color}.
        Other details are the same with Table \ref{tab:psfcolor}.
    }
        \label{tab:cmodelcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

@@

    We apply quality control to the stars and galaxies selected from the HSC UltraDeep
    COSMOS fields before we match them with the stars and models for galaxies from the 
    \hst/ACS COSMOS data. 
    The same quality control criteria are also used to select synthetic stars and 
    galaxies from the \synpipe{} results before we perform photometric comparisons.

@@

    The HSC survey defines the full--depth \& full--color regions (\texttt{FDFC}) to
    ensure the data used for science reach the expected number of exposures in each
    band
    ($\mathtt{(\#gri\ \geq\ 4)\ and\ (\#yz\ \geq\ 6)\ and\ (Limiting\ imag> 25.6)}$;
    see \citealt{HSCDR1} for details).
    Since the two \tracts{} we used in this work are almost entirely covered in
    the \texttt{FDFC} region, we did not apply this cut.

    Firstly, we make sure the object is a ``primary'' detection (in the inner part 
    of \tract{} and \texttt{patch}; not a \texttt{parent} in the deblending process), 
    is successfully deblended, has reliable centroid, and is not bothered by various 
    of optical issues:

@@

        \item[ ] \texttt{ detect\_is\_primary==True}
        \item[ ] \texttt{ deblend\_skipped==False }
        \item[ ] \texttt{ deblend\_nchild=0}
        \item[ ] \texttt{ [grizy]flags\_badcentroid==False }
        \item[ ] \texttt{ [grizy]centroid\_sdss\_flags==False }
        \item[ ] \texttt{ [grizy]flags\_pixel\_edge==False }
        \item[ ] \texttt{ [grizy]flags\_pixel\_interpolated\_center==False }
        \item[ ] \texttt{ [grizy]flags\_pixel\_saturated\_center==False }
        \item[ ] \texttt{ [grizy]flags\_pixel\_cr\_center==False }
        \item[ ] \texttt{ [grizy]flags\_pixel\_bad==False }
        \item[ ] \texttt{ [grizy]flags\_pixel\_suspect\_center==False }
        \item[ ] \texttt{ [grizy]flags\_pixel\_clipped\_any==False }
        \item[ ] \texttt{ [grizy]flags\_pixel\_bright\_object\_center==False }

    \noindent For stars, we ensure the selected objects have useful PSF magnitude:

        \item[ ] \texttt{ [grizy]flux\_psf\_flags==False }

    \noindent For galaxies, we also make sure useful \cmodel{} photometry is available:

        \item[ ] \texttt{ [grizy]cmodel\_flux\_flags==False }
